Privacy Analysis of a Mobile Sensor Application

### 2015-01-31 paper.tex
Rewrote Introduction.

\keywords{
privacy protection, IT security analysis, sensor data, mobile phones, traffic survey
}

@@

* Privacy Protection very important topic in current time Fundamental
* Fundamental trade-off between enhanced functionality and convenience
  of the service (service demands) and personal data revealed by the
  use (privacy demands).
* Challenge for service provider. Find the right balance.
* We study concrete use case of a travel-survey application.

@@

\section{Scenario Description: Mobile Traffic Survey}

\TODO{HH:\\
* System description: (Raw version copied from Privacy Analysis)\\
* Information needs of transport agency\\
}

\subsubsection{IT-Systems \& Interactions}
\label{subsubsection:it-systems}

@@

There are three stakeholders involved with the sysem: The
\emph{citizen}, the \emph{service provider} and the \emph{travel
  agency}. The service provider is the operator of all IT systems and
sells the travel-survey service to the travel agency.

>>>>

@@

The rise of mobile smart-phones equipped with a wide range of sensors
and the abundance mobile internet connectivity has paved the way to a
whole new generation of mobile services which ease the daily life of
citizens of the western developed world. Apps like Google
Maps\footnote{\url{http://google.com/maps}} allows the user to
navigate effectively in unknown cities. Others track sports activities
in order to optimize training plans or engage in virtual competitions
(e.g. Strava\footnote{Citation Needed}).

Besides the immediate benefits, citizens using these services, reveal
a wealth of which can be used to draw a very detailed picture of the
private life of the citizen. For instance, GPS location tracking can
be used to infer shopping habits or associations with political groups
(when meetings are attended). Accelerometer data can be used to detect
medical conditions like walking disabilities. All this data is highly
sensitive to the citizens privacy and can be used against the citizen
if it falls into the wrong hands.

Providers of these new services are faced with a fundamental trade-off
between features and convenience of the service and the protection of
the citizen's privacy. The service has to collect enough data to
support the basic service-promises. If too much data is collected the
privacy of the citizen is put at risk, with immediate implications for
the customer trust relation and the acceptance of the service. Also
leaks of private data can jeopardize the whole business.

In this article we study the privacy risks of a travel-survey service
for urban mobility.

@@

\section{Scenario Description: Mobile Traffic Survey}
\label{sec:ScenarioDescription}

@@

There are three stakeholders involved with the sysem: The
\emph{citizen}, the \emph{service provider} and the \emph{travel
  agency}. The service provider is the operator of all IT systems and
sells the travel-survey service to the travel agency. Figure
\ref{figure:Live+Gov Vulnerabilities} contains a schematic
visualization of the relation between these stakeholders.
